SPEI_longterm

### 2018-10-25 analysis/drought/explore_spei_longterm.Rmd
modify drought severity to include months

# Compute several indicators (drought assessments) 
da <- out3 %>% group_by(index_events) %>% 
  summarise(d_duration = unique(drought_duration),
            d_intensity = mean(spei, na.rm=TRUE),
            d_severity = sum(abs(spei), na.rm=TRUE),
            lowest_spei = min(spei),
            month_peak = month[which.min(spei)], 
            minyear = min(year),
            maxyear = max(year)) %>%
  as.data.frame()

@@

write.csv(sev12, file=here::here('data/sequias', 'severe_spei12.csv'), row.names=FALSE)

pander(sev12)
```

>>>>

# Compute several indicators (drought assessments) 
da <- out3 %>% group_by(index_events) %>% 
  summarise(d_duration = unique(drought_duration),
            d_intensity = mean(spei, na.rm=TRUE),
            d_severity = sum(abs(spei), na.rm=TRUE),
            lowest_spei = min(spei),
            month_peak = month[which.min(spei)], 
            minyear = min(year),
            maxyear = max(year),
            rangeDate = paste(month(min(date), label=TRUE), '-',
                             (month(max(date), label=TRUE)))) %>%
  as.data.frame()

@@

write.csv(sev12, file=here::here('data/sequias', 'severe_spei12.csv'), row.names=FALSE)
pander(sev12)

```

```{r}
sev6 <- sev %>% filter(variable == "spei6") %>% arrange(desc(d_duration)) %>% 
  dplyr::select(-index_events, -decade, -variable)

write.csv(sev6, file=here::here('data/sequias', 'severe_spei6.csv'), row.names=FALSE)
pander(sev6)
```

## Duration vs. Lowest SPEI (SPEI06, SPEI12)
```{r}
require(ggrepel)
# Duracion vs
sev %>% ggplot(aes(d_duration, y=lowest_spei, label=maxyear, colour=variable)) + geom_point() + 
  geom_text_repel() 
```

## Duration vs. Severity (SPEI06, SPEI12)
```{r}
sev %>% ggplot(aes(d_duration, y=d_severity, label=maxyear, colour=variable)) + geom_point() + 
  geom_text_repel() 
```

## Duration vs. Intensity (SPEI06, SPEI12)
```{r}
sev %>% ggplot(aes(d_duration, y=d_intensity, label=maxyear, colour=variable)) + geom_point() + 
  geom_text_repel() 
```

## Severity vs. Intensity (SPEI06, SPEI12)
```{r}
sev %>% ggplot(aes(d_severity, y=d_intensity, label=maxyear, colour=variable)) + geom_point() + 
  geom_text_repel() 
```
